
# Name - Aman Raj
# GRIP : The Sparks Foundation
# Data Science and Business Analytics Internship
# Task_1 : Prediction using supervised Machine Learning
# Importing data from csv file and storing it in Score
```{r}
Score <- read.csv("D:/SparksFoundation/LinearRegression.csv")
```
```{r}
Score
```

#summary of the data
```{r}
summary(Score)
```
#Scatter plot of the data
```{r}
plot(Score)
```
# Splitting the data into training and test set
```{r}
library(caTools)
```

```{r}
split <- sample.split(Score$Scores, SplitRatio=0.8)
split
```
```{r}
train <- subset(Score, split==TRUE)
test <- subset(Score, split==FALSE)
```
```{r}
train
```
```{r}
test
```

#Regression Model

```{r}
Model <- lm(Scores ~., data=train)
```

```{r}
summary(Model)
```
#Accuracy of ~ 94.5% obtained from Regression model (as given by the R-squared value)

#Prediction on the test set
```{r}
pred <- predict(Model, test)
pred
```
#comparing predcted vs actual values for the test set
```{r}
plot(test$Scores,type="l", lty=1.8, col="red") #plot of test set values
lines(pred, type="l", col="blue")
plot(pred,type="l", lty=1.8, col="blue") #plot of predicted values
```
#The Regression line with the scatter plot of given data
```{r}
plot(Score)
abline(Model)
```